---
title: "UFO Sightings and COVID-19"
author: "Group 7 - Evan Conaway, James Seidel, Sarah Derda"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
```


```{r libraries_setup, include = FALSE, eval=TRUE}

library(flexdashboard)
library(readr)
library(lubridate)
library(shiny)
library(jsonlite)
library(maptools)
library(ggplot2)
library(tidyr)
library(dplyr)
library(purrr)
library(leaflet)
library(plotly)
library(DT)
library(ggthemes)
library(viridis)
library(raster)
library(tidyverse)
library(usmap)
library(ggmap)
library(maps)
library(readxl)
library(ggrepel)
library(gridExtra)
library(dplyr)

```

```{r data_import, include = FALSE, eval=TRUE}

cases_pop_county <- read.csv("raw-data/counties_pop_casew.csv")
ufo <- read.csv("raw-data/ufo_withlatlong.csv")
USA <- getData("GADM", country = "usa", level = 2)

popup_dat <- paste0("<strong>County: </strong>", 
                    cases_pop_county$county, 
                    "<br><strong>Cases Per 100,000: </strong>", 
                    floor(cases_pop_county$casepercap))

popup_ufo <- paste0("<strong>Description: </strong>", 
                      ufo$Description)

```

### **Interactive Map**  UFO Sightings and Confirmed Cases of COVID-19 per 100,000 {data-commentary-width=300}

```{r interactive_map, eval=TRUE}

pal <- colorQuantile("YlOrRd", NULL, n = 9)
leaflet() %>% 
  addTiles() %>% 
  fitBounds(-102.03,37,-109.03, 41) %>% 
  addTiles() %>% 
  addPolygons(data = USA,
              fillColor = ~pal(cases_pop_county$casepercap), 
              fillOpacity = 0.6, 
              color = "#BDBDC3", 
              weight = 1,
              popup = popup_dat) %>% 
  addMarkers(ufo$lon, 
             ufo$lat, 
             clusterOptions = markerClusterOptions(),
             icon = makeIcon("alien.png"),
             popup = popup_ufo) %>% 
  addLegend(position = "bottomleft", pal = pal, values = cases_pop_county$casepercap,
            title = "Cases per 100,000",
            opacity = 1)

```

*** 

When first opened, the interactive map shows the parameter of Colorado. However, it shows the entire United States when zoomed outward. It's designed to be a county-level map where each county is outlined. The gradient color scale on the lower left represents confirmed COVID-19 cases per 100,000 people. The lighter the color represents less confirmed cases while the darker red color indicates higher confirmed cases per 100,000 people within that county. When the individual counties are clicked, a bubble pops up stating the name of the county along with the amount of cases. Additionally, there are multiple alien icons indicating an occurrence of at least one UFO sighting. The circles with numbers inside also indicate the number of UFO sightings, but they are condensed to avoid overlapping alien icons. When clicked, they will expand to reveal more alien icons. When the icons are clicked, the description of the UFO sighting appears.

Data sources: 

[Confirmed COVID-19 Cases](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv)
[National UFO Reporting Center](http://www.nuforc.org/webreports.html)

```{r scatterplot_framework, include = FALSE, eval=TRUE}

# Read in data
covid <- read_csv("raw-data/covidcases.csv")
ufobycounty <- read_csv("JamesWork/ufo2019counties") 

ufobycounty<- drop_na(ufobycounty)

#prepared data

ufobystate <- ufobycounty %>% 
  group_by(State) %>% 
  count() %>% 
  ungroup()

ufobystate <- mutate(.data = ufobystate, state_name = c("Alabama", "Arizona", 
                                          "Arkansas", "California", "Colorado", 
                                          "Connecticut", "Delaware", 
                                          "Florida", "Georgia","Idaho", 
                                          "Illinois", "Indiana", "Iowa", "Kansas", 
                                          "Kentucky", "Louisiana", "Maine", 
                                          "Maryland", "Massachusetts", "Michigan", 
                                          "Minnesota",
                                          "Mississippi", "Missouri", "Montana", 
                                          "Nebraska", "Nevada", "New Hampshire", 
                                          "New Jersey", "New Mexico", "New York", 
                                          "North Carolina", "North Dakota",
                                          "Ohio", "Oklahoma", "Oregon", "Pennsylvania",
                                          "Rhode Island", "South Carolina", "South Dakota", 
                                          "Tennessee", "Texas","Utah", "Vermont", 
                                          "Virginia", "Washington", "West Virginia", 
                                          "Wisconsin", "Wyoming"))

covidbystate <- covid %>% 
  group_by(state) %>% 
  count() %>% 
  ungroup() 

covidbystate <- covidbystate[-c(2, 9, 12, 13, 37, 42, 50),]

statepopulations <- read_excel("JamesWork/Statepopulations.xlsx")

ufoandcovid <- ufobystate %>%
  mutate(covid_cases = covidbystate$n) %>% 
  mutate(ufo_sightings = ufobystate$n) %>% 
  mutate(population = statepopulations$Population) %>% 
  mutate(covid_per_cap = covid_cases/population) %>% 
  mutate(ufo_per_cap = ufo_sightings/population)

##ggplots with data

ufoandcovid

statenames <- ufoandcovid$State
statenames[with(ufoandcovid, 
                !(covid_cases > 27000 | ufo_sightings > 185))] <- ""

plotone <- ufoandcovid %>% 
ggplot(aes(x=ufo_sightings, y = covid_cases)) +
  geom_point() +
  geom_text(label = statenames, size = 3, nudge_x = 18)+
  labs(title = "COVID Cases (2020) by UFO Sightings (2019) in Lower 48 states (per Capita on Right)")+
  xlab("UFO Sightings") +
  ylab("COVID Cases") +
  theme_tufte()

statenames2 <- ufoandcovid$State
statenames2[with(ufoandcovid, !(covid_per_cap > 0.01 | ufo_per_cap > 0.00005))] <- ""


plottwo <- ufoandcovid %>% 
  ggplot(aes(x=ufo_per_cap, y = covid_per_cap,)) +
  geom_point() +
  geom_text(label = statenames2, size = 3,
             position = position_nudge(x = 0.00001))+
  labs(x = "UFO Sightings per Capita", y = "COVID Cases per Capita")+
  theme_tufte() +
  theme(axis.text.x = element_blank(), axis.ticks = element_blank(),
        axis.text.y = element_blank())

#newcode

ply1 <- ggplotly(plotone)
ply2 <- ggplotly(plottwo)


```

### **Scatterplots**  COVID-19 Cases (2020) and UFO Sightings (2019) in the Lower 48 States  {data-commentary-width=300}

```{r scatterplots_final, eval=TRUE}

subplot(ply1, ply2, nrows=1)

```

*** 

The scatterplot on the left shows COVID-19 cases in 2020 (y-axis) by UFO sightings in 2019 (x-axis). Each point represents a state. The plot on the right shows the same data, but has been adjusted to display per capita measurements. Interesting states with higher COVID cases or UFO sightings, both raw and per capita adjusted, have been highlighted with the geom_text function. Visually, there appears to be no correlation between UFO sightings in 2019 and the number of COVID cases in states. 

Data sources:

[Confirmed COVID-19 Cases](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv)
[National UFO Reporting Center](http://www.nuforc.org/webreports.html)

### **Mortality Table**  Table of Total Deaths per County in the United States {data-commentary-width=300}

```{r death_table, eval= TRUE}

### This script is designed to create the data table for our flex dashboard.
### It is a table of all the Covid Deaths. It is included to remind us of everyone that has passed due 
### to this pandemic. 

covid <- read_csv("raw-data/covidcases.csv")

covid <- covid %>% 
  mutate(County = paste(covid$county,covid$state,sep = ", "))

covid <- covid %>% 
    group_by(County) %>% 
  dplyr::summarise(Deaths = last(deaths))

### This code chunk works better when knit into flexdashboard

datatable(covid, 
          colnames = c("County", "Deaths"), 
          extensions = "Scroller", style="bootstrap", 
          class="compact", width="100%", 
          options=list(deferRender=TRUE, scrollY=300, scroller=TRUE))

```

***

The following table shows each county within the United States by name on the right side with the total number of deaths in that county on the left. Confirmed cases are important in looking at the current direction of how the disease is progressing. Looking at the mortality numbers provides key information regarding the burden of the disease, which is an important consideration in deciding where to allocate resources. The search bar can be used for looking up a specific county.

Data source:

[Confirmed COVID-19 Cases](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv)
