---
title: "Testing UFO Sightings and COVID-19"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r global_options}

knitr::opts_chunk$set(echo = FALSE, 
                      warning=FALSE, 
                      message=FALSE, 
                      error=FALSE)

```

```{r libraries}

library(readr)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(forcats)
library(stringr)
library(scales)
library(broom)
library(purrr)

```

### Frame 1

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

ufo_sightings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-25/ufo_sightings.csv")

print(ufo_sightings)

```

*** 

Some commentary about Frame 1.
djsdslkfjkdsjfkldsjflkflkdsf
fksdjfjsklfjsdkljflksdfljsfkl
sjnfsdjfjksdfsljffdjflksjfjf

### Frame 2 {data-commentary-width=400}

```{r}
```

*** 

Some commentary about Frame 2.
hfksdhfjdjfhjdsfhjdhfhfjkfsf
kdfhdsjfhjksdhfhdshfhjsdhfsjfk
jdhkfjdhsjfhsdkjhfhfkjsdfhjksdhfk

### Frame 3 {data-commentary-width=400}

```{r}

```

***

This is the commentary for Fram 3.